A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-08 bioc-workflow.Rmd
all files loaded correctly

```{r removefData}
fvarLabels(hl)
fvarLabels(hl)[1:3] <- c("UniProtAccession", "UniProtID", "Description")
fvarLabels(hl)[4:6] <- paste0("Peptides.expt", 1:3)
fData(hl)[1:4, 1:6]
```

@@

```{r}
hl <- fDataToUnknown(hl, from = "Golgi apparatus", to = "unknown")
getMarkers(hl)
```

@@

## Plot the input and output
par(mfrow = c(1, 2))
plot2D(hl, fcol = "phenodisco.input", 
       main = "phenoDisco input markers", col = getStockcol()[1:6])
addLegend(hl, fcol = "phenodisco.input", cex = .7)
plot2D(hl, fcol = "pd", main = "phenoDisco output", col = cols)
addLegend(hl, fcol = "pd", cex = .7, col = cols)
```

@@

```{r loadpdRes, echo=FALSE}
svmf <- dir(extdatadir, full.names = TRUE,
              pattern = "bpw-svmopt.rds") 
params <- readRDS(svmf)
```
```{r optimise, eval=FALSE}
w <- table(getMarkers(hl, verbose = TRUE))
w <- 1/w[names(w) != "unknown"]

## 100 rounds of optimisation with five-fold cross-validation
params <- svmOptimisation(hl, fcol = "markers",
                          times = 100, xval = 5,
                          class.weights = w)
```

@@

To remove the 4 classes and create a new column of markers in the feature data called `tlmarkers` to use for the analysis:
```{r setuptlopt, eval=TRUE}
## create new markers column for tl markers
fData(hl)$tlmarkers <- fData(hl)$markers
fData(gocc)$tlmarkers <- fData(gocc)$markers

## Remove 4 classes
torm  <- c("40S Ribosome", "60S Ribosome",
           "Nucleus - Chromatin", 
           "Nucleus - Non-chromatin")
for (i in seq(torm)) {
  hl <- fDataToUnknown(hl, from = torm[i], fcol = "tlmarkers")
  gocc <- fDataToUnknown(hl, from = torm[i], fcol = "tlmarkers")
}
getMarkerClasses(hl, fcol = "tlmarkers")
getMarkerClasses(hl, fcol = "tlmarkers")
```

Optimisation stage 1: run `knnOptimisation` to get the best $k$'s for each data source.
```{r knnoptfortl, eval=FALSE}
## get best k's
kpopt <- knnOptimisation(hl, fcol = "tlmarkers")
kaopt <- knnOptimisation(gocc, fcol = "tlmarkers")
kp <- getParams(kpopt)
ka <- getParams(kaopt)
```

@@

## Now peform tl optimisation 
tlopt <- knntlOptimisation(hl, gocc,
                           fcol = "tlmarkers",
                           length.out = 4, 
                           times = 50,
                           xval = 5, k = c(kp,ka),
                           BPPARAM = par
  )
```

@@

```{r loadtlres, echo=FALSE}
tlfile <- dir(extdatadir, full.names = TRUE,
              pattern = "bpw-tlopt.rds")
tlopt <- readRDS(tlfile)

```
```{r plottl}
plot(tlopt)
```

@@

## Do the classification
hl <- knntlClassification(hl, gocc, bestTheta = bestpar, 
                          k = c(kp, ka))

>>>>

```{r removefData}
fvarLabels(hl)
fvarLabels(hl)[1:3] <- c("uniprot.accession", "uniprot.id", "description")
fvarLabels(hl)[4:6] <- paste0("peptides.expt", 1:3)
fData(hl)[1:4, 1:6]
```

@@

```{r removeGA}
hl <- fDataToUnknown(hl, from = "Golgi apparatus", to = "unknown")
getMarkers(hl)
```

@@

## Plot the input and output
par(mfrow = c(1, 2))
plot2D(hl, fcol = "phenoDisco.Input", 
       main = "phenoDisco input markers", col = getStockcol()[1:6])
addLegend(hl, fcol = "phenoDisco.Input", cex = .7)
plot2D(hl, fcol = "pd", main = "phenoDisco output", col = cols)
addLegend(hl, fcol = "pd", cex = .7, col = cols)
```

@@

```{r loadpdRes, echo=FALSE}
svmf <- dir(extdatadir, full.names = TRUE,
              pattern = "bpw-svmopt.rds") 
params <- readRDS(svmf)
```
```{r getsvmweight}
w <- table(getMarkers(hl, verbose = TRUE))
w <- 1/w[names(w) != "unknown"]
```
```{r dosvmopt, eval=FALSE}
## 100 rounds of optimisation with five-fold cross-validation
params <- svmOptimisation(hl, fcol = "markers",
                          times = 100, xval = 5,
                          class.weights = w)
```

@@

To remove the 4 classes and create a new column of markers in the feature data called `tlmarkers` to use for the analysis:
```{r loadgocc, include=FALSE}
gofile <- dir(extdatadir, full.names = TRUE,
              pattern = "bpw-gocc.rds")
gocc <- readRDS(gofile)
```
```{r setuptlopt}
## create new markers column for tl markers
fData(hl)$tlmarkers <- fData(hl)$markers
fData(gocc)$tlmarkers <- fData(gocc)$markers

## Remove 4 classes
torm  <- c("40S Ribosome", "60S Ribosome",
           "Nucleus - Chromatin", 
           "Nucleus - Non-chromatin")
for (i in seq(torm)) {
  hl <- fDataToUnknown(hl, from = torm[i], fcol = "tlmarkers")
  gocc <- fDataToUnknown(gocc, from = torm[i], fcol = "tlmarkers")
}
getMarkerClasses(hl, fcol = "tlmarkers")
getMarkerClasses(gocc, fcol = "tlmarkers")
```

Optimisation stage 1: run `knnOptimisation` to get the best $k$'s for each data source.
```{r knnoptfortl, eval=FALSE}
## get best k's
kpopt <- knnOptimisation(hl, fcol = "tlmarkers")
kaopt <- knnOptimisation(gocc, fcol = "tlmarkers")
plot(kpopt)
plot(kaopt)
```
From examining the parameter seach plots we find the best $k$'s for both the primary and auxiliary are 3.

@@

## Now peform tl optimisation 
tlopt <- knntlOptimisation(hl, gocc,
                           fcol = "tlmarkers",
                           length.out = 4, 
                           times = 50,
                           xval = 5, k = c(3, 3),
                           BPPARAM = par
  )
```

@@

```{r loadtlres, echo=FALSE}
tlfile <- dir(extdatadir, full.names = TRUE,
              pattern = "bpw-tlopt.rds")
tlopt <- readRDS(tlfile)
colnames(tlopt@results)[4] <- "Endoplasmic reticulum"
setStockcol(NULL)
```
```{r plottl}
plot(tlopt)
```

@@

## Do the classification
hl <- knntlClassification(hl, gocc, bestTheta = bestpar, 
                          k = c(3, 3))
```
